---
title: "p8105_hw1_wz2630"
output: github_document
date: "2023-09-15"
---

Problem 1
```{r}
library(moderndive)

data("early_january_weather")

# the variables in this dataset, including names / values of important variables
skimr::skim(early_january_weather)

# the size of the dataset
nrow(early_january_weather)

ncol(early_january_weather)

#the mean temperature
mean(early_january_weather$temp)

#scatterplot

ggplot(early_january_weather, aes(x = time_hour, y = temp)) + 
geom_point(aes(col = humid)) + 
labs(y = "Temperature", x = "Time", title = "Temperature at Different Times in Early January")

ggsave("scatter_plot.pdf")
```
In the early_january_weather, there are 358 observations and 15 variables. The mean of temp is 39.58.
The names of the variables are: origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, time_hour. There are many missing data in variables wind_gust and pressure. # missing data or outliers.

The variable time_hour observations are in year, month, day, and hour; temp and humid variables are in continuous numbers.


Problem 2
```{r}
df <- data.frame(random_sample = rnorm(10),
                 vec_logical = random_sample > 0,
                 vec_char = c("one", "two", "three", "four", "five", 
                                 "six", "seven", "eight", "nine", "ten"),
                 vec_factor = factor(c("medium", "low", "low", "low", "low", "high", "high", "medium", "low", "high")))

mean(df$random_sample)
mean(df$vec_logical)
```
We cannot take the mean of character variables. We can only take the mean of numerical value variables.
